Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-02 paper.tex
reproducibility intro

    \chapter{Performance}\label{performance}
        Neuroimaging frameworks are notoriously known to be compute-intensive.
        The tools and their respective workflows needed to incorporate 
        parallelism in order to save on computing time. Maintaining good 
        performance has become especially critical now that BigData has been
        introduced \weird{into the mix}. The dichotomy remains between scientific 
        workflows and BigData workflows. While scientific workflows have made
        advances towards more performant engines, they still lack the 
        strategies BigData frameworks employ to reduce data transfers.

        Another notable aspect to consider is that both types of engines 
        (scientific and BigData) are tightly coupled to the infrastructure
        they were intended to be used on. That is, as scientific workflows \tristan{use 'engine' and 'workflows' consistently (think nipype vs fmriprep).}
        try to remain efficient in their handling of compute resources, as such
        resources were previously scarce. In contrast, BigData frameworks 
        make efficient use of commodity clusters, where data transfers are 
        burdensome, particularly when faced with BigData.

@@

                    Spark and Dask can both read from filesystems available to
                    all nodes. When an action (Spark) or a compute (Dask) is 
                    called, the data is read from the storage and uploaded into
                    memory. Tasks use the data located in memory to compute the
                    results. Should data not fit in memory, the results may 
                    spill to local disk, in the instance where nodes contain
                    storage. Otherwise, the engines will spill data to shared 
                    filesystem. The later is a common case in HPC systems as 
                    storage and compute resources are typically separate, 
                    however, these shared filesystems are typically slower than 
                    local storage, and therefore, there will be additional 
                    performance penalties.

@@

                    While Spark and Dask both rely on the concept of shared 
                    memory, Spark avoids data transfers as often as possible by
                    scheduling tasks to nodes where the memory is located \tristan{You mean where RAM is available or where the data is located?}. Dask
                    , however, will schedule its tasks to the next available 
                    node.

@@

                    In contrast to MapReduce, Spark does not require data to 
                    be stored on a HDFS-like filesystem. It can read data from
                    any form of shared-filesystem, including Lustre. If data 
                    is extracted from a non HDFS-like filesystem, the initial 
                    loading of data will not use data locality. However, in all
                    future tasks in which the data is already loaded into an 
                    RDD, the scheduler will be able to assign task to the most
                    favorable partition dictated by delay scheduling \tristan{ignoring data locality?}.

@@

             Containeri
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        \section{Provenance Tracking}
        big data frameworks: limited to lineage
        \section{containerization}
    \chapter{Discussion/Conclusion}

>>>>

    \chapter{Performance}\label{performance}
        Neuroimaging frameworks are notoriously known to be compute-intensive.
        The workflows and their respective tools needed to incorporate 
        parallelism in order to save on computing time. Maintaining good 
        performance has become especially critical now that neuroimaging
        BigData has emerged. The dichotomy remains between scientific 
        workflows and BigData workflows. While scientific workflows have made
        advances towards more performant engines, they still lack the 
        strategies BigData frameworks employ to reduce data transfers.

        Another notable aspect to consider is that both types of engines 
        (scientific and BigData) are tightly coupled to the infrastructure
        they were intended to be used on. Scientific workflow engines
        try to remain efficient in their handling of compute resources since such
        resources were previously scarce. In contrast, BigData frameworks 
        make efficient use of commodity clusters, where data transfers are 
        burdensome, particularly when faced with BigData.

@@

                    Spark and Dask can both read from filesystems available to
                    all nodes. When an action (Spark) or a compute (Dask) is 
                    called, the data is read from the storage and uploaded into
                    memory. Tasks use the data located in memory to compute the
                    results. Should data not fit in memory, the results may 
                    spill to local disk, if local storage is available. 
                    Otherwise, the engines will spill data to a shared 
                    filesystem. The later is a common case in HPC systems as 
                    storage and compute resources are typically separate, 
                    however, these shared filesystems are typically slower than 
                    local storage, and therefore, there will be additional 
                    performance penalties.

@@

                    While Spark and Dask both rely on the concept of shared 
                    memory, Spark avoids data transfers as often as possible by
                    scheduling tasks to nodes where the data is located. Dask
                    , however, will schedule its tasks to the next available 
                    node.

@@

                    In contrast to MapReduce, Spark does not require data to 
                    be stored on a HDFS-like filesystem. It can read data from
                    any form of shared-filesystem, including Lustre. If data 
                    is extracted from a non HDFS-like filesystem, the initial 
                    loading of data will not use data locality. However, in all
                    future tasks in which the data is already loaded into an 
                    RDD, the scheduler will be able to assign task to the most
                    favorable partition dictated by delay scheduling according
                    to data locality.

@@

             Containeri
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        Reproducibility is a vital component to all scientific workflows. 
        Without reproducibility, correctness of results could never be 
        determined. Reproducibility is defined as the ability to obtain similar 
        results by 
        recreating or executing the original workflow on the same or different
        infrastructure\note{cite}. It have been found that more than 70\% of
        scientific experiments are not reproducible \note{cite Mbaker}

        Current studies show that different tools 
        performing the same function, in addition to the same versions of tools 
        executing on top of different operating systems produce significantly 
        dissimilar results. As a result, it is necessary that specific details 
        on the workflow, such a data used, software versions and operating 
        system used are provided. For this reason, many workflow engines have
        incorporated provenance tracking into their design.

        Getting specific versions of tools and their workflows is not always 
        a straightforward process. To facilitate this, many workflow engines
        have begun to use containers to ensure that users can reproduce the 
        experiment within a contained environment identical to the one it that
        was originally experimented on.

        This chapter will examine how different workflow engines tackle the 
        issue of reproducibility. Section~\ref{prov} will discuss how the 
        engines assimilate and distribute the provenance data. 
        Section~\ref{repcont} will examine how these engines use containers to
        facilitate reproducibility of the experiments.
        \section{Provenance Tracking}\label{prov}

        \section{Containerization}\label{repcont}
    \chapter{Discussion/Conclusion}
